Procrastination and Dementia

### 2025-09-29 README.qmd
Woops :bug:

>>>>

## Procrastination as a Marker of Cognitive Decline: Evidence from Longitudinal Transitions in the Older Adult Population

- [Cormac Monaghan](https://c-monaghan.github.io/) • Maynooth University
- [Rafael de Andrade Moral](https://rafamoral.github.io/) • Maynooth University
- [Michelle Kelly](https://www.ncirl.ie/About/A-Z-Staff-Directory/Staff/346) • National College of Ireland
- [Joanna McHugh Power](https://www.maynoothuniversity.ie/people/joanna-mchugh-power) • Maynooth University
